Untitled

### 2023-09-11 code/analysis_Redo.Rmd
triangle of distance

df.p %>% 
  filter(Year.y == Att.z) %>% 
  group_by(ClinicType) %>% 
  select(Area.km2:popcenter.y) %>% 
  summarise_all(mean.nas)
```

>>>>

df.p %>% 
  filter(Year.y == Att.z) %>% 
  group_by(ClinicType) %>% 
  select(Area.km2:popcenter.y) %>% 
  summarise_all(mean.nas)

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>% 
  mutate(DistRivaltoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), DistRivaltoCenter = mean.nas(DistRivaltoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>% 
  mutate(DistIncumbtoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(Radius = mean.nas(Radius), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))

df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Incumbent") %>%
  select(Zip, xcoor, ycoor) %>% 
  full_join(df.p %>% 
  filter(Year.y == Att.z) %>% 
  filter(ClinicType == "Rival") %>%
  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
  #group_by(Zip) %>% 
  summarise(DistIncumbtoRival = mean.nas(DistIncumbtoRival))
